Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-07-14 Paperfolder/Paperfolder.Rmd
updated ready to share with Yatsuya

  ``C.W. and H.Y. conceive and designed the study; C.W. analyzed the data; C.W. wrote the first draft of the paper. A.T. provided the database. All of the authors approved and finalized the manuscript for publication.''

@@

kable(dt, format = "latex", caption = "Sex-specific baseline characteristics according to the frequency of milk intake.", booktabs = T,linesep = "") %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
  add_header_above(c(" ", "", "", "Milk drinkers" = 4, "")) %>%
  # add_indent(c(4:6, 8:11, 14:17, 19, 20, 22:25, 27:30, 32:35, 37:39, 41:43, 45, 47, 49, 51, 53, 55)) %>%
  pack_rows("Men (n = 39386)", 1, 16) %>%
  pack_rows("Women (n = 545999)", 17, 32) #%>% 
  # footnote(c("Abbreviations: n, number; SD, standard deviation; Alc_Fre, alcohol intake; BMI, Body Mass Index; Slepgrp, sleep duration", "groups; Veg, vegetable intake; Coffe, coffee intake; DM/HT/KID/LIV_hist, diabetes, hypertension, kidney disease,", "liver disease history."))
```

@@

 & \textbf{Never} & \textbf{Drinker} & \textbf{1-2 times/} & \textbf{1-2 times/} & \textbf{3-4 times/} & \textbf{Almost} & \\

@@

In the JACC study cohort, our analysis showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction. Our evidence also suggested that stroke mortality events were delayed among Japanese male daily milk consumers compared with non-consumers.

In conclusion, the JACC study database has provided evidence that Japanese men who consumed milk daily had lower hazard of dying from stroke especially cerebral infarction compared with their counterparts who never consumed milk. Time before an event of stroke mortality occurred were slowed down and delayed among those who drank milk regularly.

\begin{table}[!h]

@@

\begin{table}[!h]

@@

>>>>

  ``C.W. and H.Y. conceived and designed the study; C.W. analyzed the data; C.W. wrote the first draft of the paper. A.T. provided the database. All of the authors approved and finalized the manuscript for publication.''

@@

kable(dt, format = "latex", caption = "Sex-specific baseline characteristics according to the frequency of milk intake.", booktabs = T,linesep = "") %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
  add_header_above(c(" ", "", "", "Milk drinkers" = 4, "")) %>%
  # add_indent(c(4:6, 8:11, 14:17, 19, 20, 22:25, 27:30, 32:35, 37:39, 41:43, 45, 47, 49, 51, 53, 55)) %>%
  pack_rows("Men (n = 39386)", 1, 16) %>%
  pack_rows("Women (n = 54999)", 17, 32) #%>% 
  # footnote(c("Abbreviations: n, number; SD, standard deviation; Alc_Fre, alcohol intake; BMI, Body Mass Index; Slepgrp, sleep duration", "groups; Veg, vegetable intake; Coffe, coffee intake; DM/HT/KID/LIV_hist, diabetes, hypertension, kidney disease,", "liver disease history."))
```

@@

 & \textbf{Never} & \textbf{Drinkers} & \textbf{1-2 times/} & \textbf{1-2 times/} & \textbf{3-4 times/} & \textbf{Almost} & \\

@@

In the JACC study cohort, our analyses showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction. Our evidence also suggested that stroke mortality events were delayed among Japanese male daily milk consumers compared with non-consumers.

\begin{table}[H]

@@

\begin{table}[H]

@@

In conclusion, the JACC study database has provided evidence that Japanese men who consumed milk daily had lower hazard of dying from stroke especially cerebral infarction compared with their counterparts who never consumed milk. Time before an event of stroke mortality occurred were slowed down and delayed among men who drank milk regularly.

### 2020-07-14 paprfolder_docx/strokeJACC.Rmd
updated ready to share with Yatsuya

In the JACC study cohort, our analysis showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction. Our evidence also suggested that stroke mortality events were delayed among Japanese male daily milk consumers compared with non-consumers.

@@

In conclusion, the JACC study database has provided evidence that Japanese men who consumed milk daily had lower hazard of dying from stroke especially cerebral infarction compared with their counterparts who never consumed milk. Time before an event of stroke mortality occurred were slowed down and delayed among those who drank milk regularly.

>>>>

In the JACC study cohort, our analyses showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction. Our evidence also suggested that stroke mortality events were delayed among Japanese male daily milk consumers compared with non-consumers.

@@

In conclusion, the JACC study database has provided evidence that Japanese men who consumed milk daily had lower hazard of dying from stroke especially cerebral infarction compared with their counterparts who never consumed milk. Time before an event of stroke mortality occurred were slowed down and delayed among men who drank milk regularly.
